Software Citation Principles

### 2016-07-21 sc-principles/software-citation-principles.tex
moving bits around and new section for better structure

@@

These software citation principles were originally based on an adaptation of the
FORCE11 Data Citation Principles~\cite{data-citation-principles}, and then were
modified based on discussions of the FORCE11 Software Citation Working
Group (see Appendix~\ref{app:wg_members} for members), information from the use
cases in \S\ref{sec:use_cases}, and the related work in \S\ref{sec:related_work}.
The adaptations have been made
because software, while similar to data in terms of not traditionally having
been cited in publications, is also different than data in that it can be used
to express or explain concepts, it is updated more frequently, and it is
executable.
% \katznote{are there any other difference between software and data that should be stated here?}
Also, while software can be considered a type of data, the converse is not
generally true.

@@

@@

@@

We have documented and analyzed a set of use cases related to software citation
in \cite{SC-Use-Cases}. Table~\ref{tab:use_cases} summarizes these use cases and
makes clear what the requirements are for software citation in each case.
Each example represents a particular stakeholder performing an activity related to citing software, with the given metadata as information needed to do that.
In that table,
we use the following definitions:
\begin{itemize}

>>>>

\niemnote{Do we want a better introduction, to help with the structure of the paper?}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Process of creating principles}
\label{sec:process}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The software citation principles were originally based on an adaptation of the
FORCE11 Data Citation Principles~\cite{data-citation-principles}, and
modified based on discussions of the FORCE11 Software Citation Working
Group (see Appendix~\ref{app:wg_members} for members), information from the use
cases in \S\ref{sec:use_cases}, and the related work in \S\ref{sec:related_work}.
The adaptations were made because software, while similar to data in terms of
not traditionally having been cited in publications, is also different than
data. Software can be used to express or explain concepts, it is typically
updated more frequently than data\footnote{Datasets can of course be frequently
updated, but each update likely represents the findings of a new or repeated
study.}, and it is executable.
\niemnote{Dan: can you add more here?}
Also, while software can be considered a type of data, the converse is not
generally true.

@@

We documented and analyzed a set of use cases related to software citation
in \cite{SC-Use-Cases} (recorded in Appendix~\ref{app:usecases} for completeness).
Table~\ref{tab:use_cases} summarizes these use cases and
makes clear what the requirements are for software citation in each case.
Each example represents a particular stakeholder performing an activity
related to citing software, with the given metadata as information needed to
do that. In that table, we use the following definitions:
\begin{itemize}
